Dissecting Neural Style Transfer

### 2019-05-26 paper/paper.tex
1

\keywords{Neural network, Deep learning, 
Small data, Interpretability, Network pruning, Network reduction.}
\end{abstract}

@@

It is necessary to point out that a deep neural network that neural style transfer
is concerend about
is just a sequence of functions
$F_1,F_2,F_3,...$
whose inputs and outputs are all multi-dimensional arrays, as illustrated in Figure \ref{f1f2f3}.
\begin{figure}
\center
\includegraphics[width=0.6\textwidth]{f1f2f3.pdf}
\caption{A deep neural network \label{f1f2f3}}
\end{figure}
Because the arrays have usually more than two numbers of dimensions
they are not really matrices.
The arrays are called tensors (as in TensorFlow or torch.Tensor in PyTorch) 
but actual tensor algebra in a mathematical sense is rarely relevant.
The functions need to be differentiable, which is handled automatically by modern 
deep learning frameworks.
Other than that we can treat the functions as blackboxes because we are 
not concerned of training the model.

For the vgg19 model that most neural style transfer implementations available are based on,
The inputs and outpus of each layer are all arrays with 4 dimensions.
The word ``dimension'' here may mean something slightly different from what ``dimension'' means in
for example ``$3$-dimension vector''. 
Some people call the number of dimensions ``rank'' which would then raise another confusion with the rank of matrices.

@@

The 2nd dimension is the ``feature'' dimension. For a raw RGB image, it is 3.
Intermediate values between, for example, $F_3$ and $F_4$, usually 
have a size much larger than 3, such as 64 or 128

>>>>

\keywords{Neural network, Deep learning, 
Small data, Interpretability .}
\end{abstract}

@@

It is necessary to point out that a deep neural network that neural style transfer
is concerend about
is just a sequence of functions
$F_1,F_2,F_3,...$
whose inputs and outputs are all multi-dimensional arrays, as illustrated in Figure \ref{f1f2f3}.
\begin{figure}
\center
\includegraphics[width=0.6\textwidth]{f1f2f3.pdf}
\caption{A deep neural network \label{f1f2f3}}
\end{figure}
Because the arrays have usually more than two numbers of dimensions
they are not really matrices.
The arrays are called tensors (as in TensorFlow or torch.Tensor in PyTorch) 
but actual tensor algebra in a mathematical sense is rarely relevant.
The functions need to be differentiable, which is handled automatically by modern 
deep learning frameworks.
Other than that we can treat the functions as blackboxes because we are 
not concerned of training the model.
A ``layer'' in a deep neural network refers to a few consecutive functions together.
It is not particularly necessary to consider ``layers'' in this work. 
Though it is important to note that in our illustrations there are functions instead of layers.

\subsection{vgg19 model}
For the vgg19 model that most neural style transfer implementations available are based on,
The inputs and outpus of each layer are all arrays with 4 dimensions.
The word ``dimension'' here may mean something slightly different from what ``dimension'' means in
for example ``$3$-dimension vector''. 
Some people call the number of dimensions ``rank'' which would then raise another confusion with the rank of matrices.
We give an illustration for the vgg19 model in Figure \ref{vgg512}
\begin{figure}
\center
\includegraphics[width=\textwidth]{vgg512.pdf}
\caption{The VGG19 model with an $512\times512$ RGB image as its input \label{vgg512}}
\end{figure}

@@

The 2nd dimension is the ``feature'' dimension. For a raw RGB image, it is 3.
Intermediate arrays between, for example, $F_3$ and $F_4$, usually 
have a size much larger than 3, such as 64 or 128.

The 3nd and 4th dimensions are just spatial locations. 
For a $512\times512$ image they are 512 and 512. 
For intermediate arrays, these 2 dimensions are sometimes scaled down
to half or even $\frac{1}{4}$ of the sizes of the image.

The functions $F_1,F_2,F_3,...$ now have meaningful names such as relu\_1, conv\_2 now.
[Not actually necessary to know but insert your elaborations here]

The arrays after the initial image are called feature maps, because their value means
``how much a feature x exists at position y and x''.
For example in a $1\times64\times512\times512$ feature map, it means there are 64 types of features.
and its [1, 17, 111, 222] element, would then mean the extent that the 17th type feature exists
at the 111 row and 222 column position of the image.
